---
title: "Biking Correlations"
author: "Felix A. Baez Santiago"
date: '2022-07-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
```

```{r}
hhmem <- read_excel("biking.xlsx", sheet = "HouseHoldMembers") %>% arrange(City)
bikedata <- read_excel("biking.xlsx", sheet = "Bike8bData") %>% arrange(Town)
income <- read_excel("biking.xlsx", sheet = "Income") %>% arrange(Cities)
age <- read_excel("biking.xlsx", sheet = "Age") %>% arrange(City)
marital <- read_excel("biking.xlsx", sheet = "Marital Status") %>% arrange(City)
biking_complete <- read_excel("biking.xlsx", sheet = "BikeTrails") %>%arrange(Cities)
```

Correlations between biking habits and Mean Income
```{r}
cor(bikedata$`Get to Work`, bikedata$MeanIncome)
cor(bikedata$`For Exercise`, bikedata$MeanIncome)
cor(bikedata$`For Enjoyment`, bikedata$MeanIncome)
cor(bikedata$`For Basic Needs`, bikedata$MeanIncome)
```
0.1340277
0.3217055
0.4515306
-0.01408556
Correlations between biking habits and Household size
```{r}
cor(bikedata$`Get to Work`, bikedata$`HH Size`)
cor(bikedata$`For Exercise`, bikedata$`HH Size`)
cor(bikedata$`For Enjoyment`, bikedata$`HH Size`)
cor(bikedata$`For Basic Needs`, bikedata$`HH Size`)
```
-0.05152124
0.04111465
-0.04578838
0.2105496
Correlations between biking habits and single marital status
```{r}
cor(marital$Single, bikedata$`Get to Work`)
cor(marital$Single, bikedata$`For Exercise`)
cor(marital$Single, bikedata$`For Enjoyment`)
cor(marital$Single, bikedata$`For Basic Needs`)
```
0.2212685
0.07930735
0.3037017
0.4365965
Correlations between biking habits and divorced marital status
```{r}
cor(marital$`Divorced/Separated`, bikedata$`Get to Work`)
cor(marital$`Divorced/Separated`, bikedata$`For Exercise`)
cor(marital$`Divorced/Separated`, bikedata$`For Enjoyment`)
cor(marital$`Divorced/Separated`, bikedata$`For Basic Needs`)
```
0.4052648
0.0104096
0.05856581
-0.2419803
Correlations between biking habits and married marital status
```{r}
cor(marital$`Married or living as married`, bikedata$`Get to Work`)
cor(marital$`Married or living as married`, bikedata$`For Exercise`)
cor(marital$`Married or living as married`, bikedata$`For Enjoyment`)
cor(marital$`Married or living as married`, bikedata$`For Basic Needs`)
```
-0.39027
-0.03683036
-0.2439611
-0.1152611
Correlations between biking habits and widowed marital status
```{r}
cor(marital$Widowed, bikedata$`Get to Work`)
cor(marital$Widowed, bikedata$`For Exercise`)
cor(marital$Widowed, bikedata$`For Enjoyment`)
cor(marital$Widowed, bikedata$`For Basic Needs`)
```
0.2398713
0.01217716
0.2219662
0.1750913
Correlations between biking habits and age
```{r}
cor(age$`Mean Age`, bikedata$`Get to Work`)
cor(age$`Mean Age`, bikedata$`For Exercise`)
cor(age$`Mean Age`, bikedata$`For Enjoyment`)
cor(age$`Mean Age`, bikedata$`For Basic Needs`)
```
0.2228982
0.06029007
0.1499271
0.08225028
Correlations between bike trail preferences and biking habits
```{r}
cor(biking_complete$Trees, bikedata$`Get to Work`)
cor(biking_complete$Trees, bikedata$`For Exercise`)
cor(biking_complete$Trees, bikedata$`For Enjoyment`)
cor(biking_complete$Trees, bikedata$`For Basic Needs`)
```
-0.3343898
0.06398206
0.1069677
0.1333669
```{r}
cor(biking_complete$light, bikedata$`Get to Work`)
cor(biking_complete$light, bikedata$`For Exercise`)
cor(biking_complete$light, bikedata$`For Enjoyment`)
cor(biking_complete$light, bikedata$`For Basic Needs`)
```
-0.1643146
0.06963945
0.008650896
0.229224
```{r}
cor(biking_complete$sit, bikedata$`Get to Work`)
cor(biking_complete$sit, bikedata$`For Exercise`)
cor(biking_complete$sit, bikedata$`For Enjoyment`)
cor(biking_complete$sit, bikedata$`For Basic Needs`)
```
0.06383537
0.06394473
0.2502892
-0.0290712
```{r}
cor(biking_complete$`well kept`, bikedata$`Get to Work`)
cor(biking_complete$`well kept`, bikedata$`For Exercise`)
cor(biking_complete$`well kept`, bikedata$`For Enjoyment`)
cor(biking_complete$`well kept`, bikedata$`For Basic Needs`)
```
-0.2296765
0.2089254
0.1101076
0.2379067
```{r}
cor(biking_complete$bike, bikedata$`Get to Work`)
cor(biking_complete$bike, bikedata$`For Exercise`)
cor(biking_complete$bike, bikedata$`For Enjoyment`)
cor(biking_complete$bike, bikedata$`For Basic Needs`)
```
0.1520621
0.07939742
0.2027569
0.1415885
```{r}
cor(biking_complete$stop, bikedata$`Get to Work`)
cor(biking_complete$stop, bikedata$`For Exercise`)
cor(biking_complete$stop, bikedata$`For Enjoyment`)
cor(biking_complete$stop, bikedata$`For Basic Needs`)
```
0.08304388
0.2720578
0.2057022
0.1911731
```{r}
cor(biking_complete$rest, bikedata$`Get to Work`)
cor(biking_complete$rest, bikedata$`For Exercise`)
cor(biking_complete$rest, bikedata$`For Enjoyment`)
cor(biking_complete$rest, bikedata$`For Basic Needs`)
```
-0.1631422
0.1565275
0.1594873
-0.04802635
```{r}
cor(biking_complete$business, bikedata$`Get to Work`)
cor(biking_complete$business, bikedata$`For Exercise`)
cor(biking_complete$business, bikedata$`For Enjoyment`)
cor(biking_complete$business, bikedata$`For Basic Needs`)
```
0.308335
-0.05263546
0.1280462
0.3352066
```{r}
cor(biking_complete$nature, bikedata$`Get to Work`)
cor(biking_complete$nature, bikedata$`For Exercise`)
cor(biking_complete$nature, bikedata$`For Enjoyment`)
cor(biking_complete$nature, bikedata$`For Basic Needs`)
```
0.1104077
-0.07094732
0.2618759
-0.01588026
```{r}
cor(biking_complete$Countryside, bikedata$`Get to Work`)
cor(biking_complete$Countryside, bikedata$`For Exercise`)
cor(biking_complete$Countryside, bikedata$`For Enjoyment`)
cor(biking_complete$Countryside, bikedata$`For Basic Needs`)
```
0.2267602
-0.1296485
0.04357034
-0.03686961
```{r}
cor(biking_complete$trail, bikedata$`Get to Work`)
cor(biking_complete$trail, bikedata$`For Exercise`)
cor(biking_complete$trail, bikedata$`For Enjoyment`)
cor(biking_complete$trail, bikedata$`For Basic Needs`)
```
-0.09166087
-0.1277117
0.01474238
0.06823977
```{r}
cor(biking_complete$bird, bikedata$`Get to Work`)
cor(biking_complete$bird, bikedata$`For Exercise`)
cor(biking_complete$bird, bikedata$`For Enjoyment`)
cor(biking_complete$bird, bikedata$`For Basic Needs`)
```
0.1063735
-0.04321706
0.2346582
-0.2050788





















